\vspace*{-8mm}\textbf{\textsc{Novelty Detection for Semantic Place Categorization}}

### 2011-06-26 thesis/novelty-intro.tex
small typo

\subsection{Probability Ratio Comparison}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
First, the performance of the novelty threshold selection was plotted for a set
of 1000 samples taken from the whole distribution (\autoref{fig:synthetic-roc}).
The samples where uniformly generated by graphs with 5, 10, 15, 20, 35, 50 features.
Additionally the feature types were also uniformly sampling, for that it is possible
that in certain samples some feature types were sensed more than once and other were not
sensed at all.
This was chosen to mimic
the dynamic properties expected to see when implemented on a robot.

>>>>

\subsection{Probability Ratio Comparison}
%%% Results 1
% Show the threshold ratio is an optimal detector (if perfect information was available)
% Show that the thresholds are suitable functions for implementing a static threshold.
First, the performance of the novelty threshold selection was plotted for a set
of 1000 samples taken from the whole distribution (\autoref{fig:synthetic-roc}).
The samples where uniformly generated by graphs with 5, 10, 15, 20, 35, 50 features.
Additionally the feature types were also uniformly sampled, for that it is possible
that in certain samples some feature types were sensed more than once and other were not
sensed at all.
This was chosen to mimic
the dynamic properties expected to see when implemented on a robot.
